---
title: "LinearRegressionAnalysis"
author: "Michael Phillips"
date: "3/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive Summary

* Aids is a huge predictor of low life expectancy in developing countries, but not at all in developed.

* BMI is important in developing countries (lower BMI -> lower life expectancy) but not in developed. Adolescent thinness is associated with lower life in developed countries. This all is evidence that worldwide there is a much bigger problem with undernourishment than with obesity.

* Schooling is important indicator for both sets, but extremely important for developing countries.


## All Data

First I grouped all data together from the kaggle dataset.

```{r echo=FALSE}
df_kaggle <- read.csv("Life_Expectancy_Data.csv", header = T, stringsAsFactors = T)
model_all <- lm(data=df_kaggle, formula=Life.expectancy~Status + Alcohol+percentage.expenditure+BMI + 
              GDP + HIV.AIDS + Diphtheria + thinness.5.9.years  + 
              Income.composition.of.resources + Schooling)
summary(model_all)
par(mfrow=c(2,2))
termplot(model_all)


```

From this it looks like HIV.AIDS, Schooling, and Income Composition are the biggest effects.

Then I wanted to break it up into developed vs developing and see if
any different trends.


## Developed Countries

```{r echo=FALSE}
df_developed <- subset(df_kaggle, df_kaggle$Status=="Developed")
model.developed <- lm(data=df_developed, formula=Life.expectancy~Alcohol+
                        thinness..1.19.years + 
                        Income.composition.of.resources + Schooling)
summary(model.developed)
par(mfrow=c(2,2))
termplot(model.developed)


```

## Developing Countries

```{r echo=FALSE}
df_developing <- subset(df_kaggle, df_kaggle$Status=="Developing")
model.developing <- lm(data=df_developing, formula=Life.expectancy~Alcohol+percentage.expenditure+BMI + 
                         GDP +HIV.AIDS + Diphtheria + thinness.5.9.years  + 
                         Income.composition.of.resources + Schooling)
summary(model.developing)
par(mfrow=c(2,2))
termplot(model.developing)
```


## Takeaways

* Aids is a huge predictor of low life expectancy in developing countries, but not at all in developed.

* BMI is important in developing countries (lower BMI -> lower life expectancy) but not in developed. Adolescent thinness is associated with lower life in developed countries. This all is evidence that worldwide there is a much bigger problem with undernourishment than with obesity.

* Schooling is important indicator for both sets, but extremely important for developing countries.

